Global code motion of congruent instructions

### 2017-04-18 paper.tex
split some long lines

\begin{verbatim}
void doCodeSinking()
  For each value number VN with 2 or more instructions
    if there are two instructions with same immediate successor as post-dominator
      if both are only used in the same PHI-node (PN) of the successor
        if both have dependencies that are available or can be made available at the sink point
           mark VN as sinkable
  For each pair (I1, I2) of sinkable instructions
    Move I1 to the sink point which is just after all the PHI-nodes in the post-dominator
    update all the uses of PHI node (PN) with I1
    Remove I2 and PN
    if I1 is a memory reference:
      update MemorySSA of I1 and others to point to the MemorySSA reference of I1
      remove MemorySSA reference of all others which were deleted
    update statistics
\end{verbatim}

@@

\section{Experimental Evaluation}
\label{sec:experimental-results}
% Experimental results: Register spills, compile time, run time. compile-time comparison w.r.t. gcc
For evaluation of \gcm{}, we built \SPEC{} with the patch. All the experiments
were conducted on an \xlinux{} machine and at -Ofast optimization level. Each
sub benchmark was run three times and the best result was taken. We collected
execution time and code-size which is listed in Table~\ref{tab:code-size}, other
compiler stats are listed in Table~\ref{tab:spills}, Table~\ref{tab:stats}, and
Table~\ref{tab:code-motion-metric}.  We also measured compile time
Table~\ref{tab:compile-time} to see the impact of \gcm{}.

>>>>

\begin{verbatim}
void doCodeSinking()
  For each value number VN with 2 or more instructions
    if there are two instructions with same immediate successor as post-dominator
      if both are only used in the same PHI-node (PN) of the successor
        if both have dependencies that are available at the sink point
           // available or can be made available by rematerialization
           mark VN as sinkable
  For each pair (I1, I2) of sinkable instructions
    Move I1 to the sink point
    // the sink point is just after all the PHI-nodes in the post-dominator
    update all the uses of PHI node (PN) with I1
    Remove I2 and PN
    if I1 is a memory reference:
      update MemorySSA of I1 and others to point to the MemorySSA reference of I1
      remove MemorySSA reference of all others which were deleted
    update statistics
\end{verbatim}

@@

\section{Experimental Evaluation}
\label{sec:experimental-results}
% Experimental results: Register spills, compile time, run time. compile-time comparison w.r.t. gcc
For evaluation of \gcm{}, we built \SPEC{} with the patch. All the experiments
were conducted on an \xlinux{} machine and at -Ofast optimization level. Each
benchmark was run three times and the best result was taken. We collected
execution time and code-size which is listed in Table~\ref{tab:code-size}, other
compiler statistics are listed in Table~\ref{tab:spills}, Table~\ref{tab:stats}, and
Table~\ref{tab:code-motion-metric}.  We also measured compile time
Table~\ref{tab:compile-time} to see the impact of \gcm{}.
